---
title: "Reliability_self"
author: "Chang Lu"
date: "2025-05-12"
output: pdf_document
---

```{r}
library(dplyr)
library(psych)
library(tidyverse)
library(modelsummary)
```

data preparation - self-reported bfi
```{r}
df_self <- read.csv("~/Desktop/conversation/SCFIS-Zoom_Initial_W1_SharedReality 1.csv")

bfi_self <- df_self %>%
  select(PID, I_bfi10_findsfault, I_bfi11_thorough, I_bfi12_depressed, I_bfi13_original, I_bfi21_reserved, 
         I_bfi14_unselfish, I_bfi15_careless, I_bfi16_relaxed, I_bfi1_energy, I_bfi18_quarrels, 
         I_bfi19_reliable, I_bfi20_tense, I_bfi22_deepthinker, I_bfi3_enthusiasm, I_bfi23_forgiving, 
         I_bfi5_quiet, I_bfi7_assertive, I_bfi8_shy, I_bfi4_calm, I_bfi9_outgoing, I_bfi6_makesplans
  ) %>%
  rename(
    bfi_2 = I_bfi10_findsfault,
    bfi_3 = I_bfi11_thorough,
    bfi_4 = I_bfi12_depressed,
    bfi_5 = I_bfi13_original,
    bfi_6 = I_bfi21_reserved,
    bfi_7 = I_bfi14_unselfish,
    bfi_8 = I_bfi15_careless,
    bfi_9 = I_bfi16_relaxed,
    bfi_11 = I_bfi1_energy,
    bfi_12 = I_bfi18_quarrels,
    bfi_13 = I_bfi19_reliable,
    bfi_14 = I_bfi20_tense,
    bfi_15 = I_bfi22_deepthinker,
    bfi_16 = I_bfi3_enthusiasm,
    bfi_17 = I_bfi23_forgiving,
    bfi_21 = I_bfi5_quiet,
    bfi_26 = I_bfi7_assertive,
    bfi_31 = I_bfi8_shy,
    bfi_34 = I_bfi4_calm,
    bfi_36 = I_bfi9_outgoing,
    bfi_38 = I_bfi6_makesplans
  )

#reverse-coded items
bfi_self$bfi_2R <- 6 - bfi_self$bfi_2
bfi_self$bfi_6R <- 6 - bfi_self$bfi_6
bfi_self$bfi_8R <- 6 - bfi_self$bfi_8
bfi_self$bfi_9R <- 6 - bfi_self$bfi_9
bfi_self$bfi_12R <- 6 - bfi_self$bfi_12
bfi_self$bfi_21R <- 6 - bfi_self$bfi_21
bfi_self$bfi_31R <- 6 - bfi_self$bfi_31
bfi_self$bfi_34R <- 6 - bfi_self$bfi_34


bfi_self <- bfi_self %>%
  select(-c(bfi_2, bfi_6, bfi_8, bfi_9, bfi_12, 
            bfi_21, bfi_31, bfi_34))
```

**Extraversion**
extraversion items: 
bfi_6R + bfi_11 + bfi_16 + bfi_21R + bfi_26 + bfi_31R + bfi_36
```{r}
# Get means and variances
mv <- datasummary(bfi_6R + bfi_11 + bfi_16 + bfi_21R + bfi_26 + bfi_31R + bfi_36 ~ Mean + Var, data = bfi_self,
                  output = "data.frame")

# Correlation, adding means and variances
datasummary_correlation(bfi_self[c("bfi_6R", "bfi_11", "bfi_16", "bfi_21R", "bfi_26", "bfi_31R", "bfi_36")],
                        add_columns = mv[-1])
```

```{r}
psych::alpha(bfi_self[c("bfi_6R", "bfi_11", "bfi_16", "bfi_21R", "bfi_26", "bfi_31R", "bfi_36")])
```

**Agreeableness**
agreeableness items:
bfi_2R + bfi_7 + bfi_12R + bfi_17 
```{r}
# Get means and variances
mv <- datasummary(bfi_2R + bfi_7 + bfi_12R + bfi_17 ~ Mean + Var, data = bfi_self,
                  output = "data.frame")

# Correlation, adding means and variances
datasummary_correlation(bfi_self[c("bfi_2R", "bfi_7", "bfi_12R", "bfi_17")],
                        add_columns = mv[-1])

```

```{r}
psych::alpha(bfi_self[c("bfi_2R", "bfi_7", "bfi_12R", "bfi_17")])
```

**Conscientiousness**
Conscientiousness items: 
bfi_3 + bfi_8R + bfi_13 + bfi_38
```{r}
# Get means and variances
mv <- datasummary(bfi_3 + bfi_8R + bfi_13 + bfi_38 ~ Mean + Var, data = bfi_self,
                  output = "data.frame")

# Correlation, adding means and variances
datasummary_correlation(bfi_self[c("bfi_3", "bfi_8R", "bfi_13", "bfi_38")],
                        add_columns = mv[-1])
```

```{r}
psych::alpha(bfi_self[c("bfi_3", "bfi_8R", "bfi_13", "bfi_38")])
```

**Neuroticism**
Neuroticism items:
bfi_4 + bfi_9R + bfi_14 + bfi_34R
```{r}
# Get means and variances
mv <- datasummary(bfi_4 + bfi_9R + bfi_14 + bfi_34R ~ Mean + Var, data = bfi_self,
                  output = "data.frame")

# Correlation, adding means and variances
datasummary_correlation(bfi_self[c("bfi_4", "bfi_9R", "bfi_14", "bfi_34R")],
                        add_columns = mv[-1])
```

```{r}
psych::alpha(bfi_self[c("bfi_4", "bfi_9R", "bfi_14", "bfi_34R")])
```

***Other-reported***
```{r}
df_other <- read.csv("~/Desktop/conversation/SCFIS-Zoom_RR_Final_W1_SharedReality.csv")

bfi_other <- df_other %>%
  select(PID, TID, Order,
         P_bfi10_findsfault, P_bfi11_thorough, P_bfi12_depressed, P_bfi13_original, P_bfi21_reserved, 
         P_bfi14_unselfish, P_bfi15_careless, P_bfi16_relaxed, P_bfi1_energy, P_bfi18_quarrels, 
         P_bfi19_reliable, P_bfi20_tense, P_bfi22_deepthinker, P_bfi3_enthusiasm, P_bfi23_forgiving, 
         P_bfi5_quiet, P_bfi7_assertive, P_bfi8_shy, P_bfi4_calm, P_bfi9_outgoing, P_bfi6_makesplans
  ) %>%
  rename(
    bfi_2 = P_bfi10_findsfault,
    bfi_3 = P_bfi11_thorough,
    bfi_4 = P_bfi12_depressed,
    bfi_5 = P_bfi13_original,
    bfi_6 = P_bfi21_reserved,
    bfi_7 = P_bfi14_unselfish,
    bfi_8 = P_bfi15_careless,
    bfi_9 = P_bfi16_relaxed,
    bfi_11 = P_bfi1_energy,
    bfi_12 = P_bfi18_quarrels,
    bfi_13 = P_bfi19_reliable,
    bfi_14 = P_bfi20_tense,
    bfi_15 = P_bfi22_deepthinker,
    bfi_16 = P_bfi3_enthusiasm,
    bfi_17 = P_bfi23_forgiving,
    bfi_21 = P_bfi5_quiet,
    bfi_26 = P_bfi7_assertive,
    bfi_31 = P_bfi8_shy,
    bfi_34 = P_bfi4_calm,
    bfi_36 = P_bfi9_outgoing,
    bfi_38 = P_bfi6_makesplans
  )

#reverse-coded items
bfi_other$bfi_2R <- 6 - bfi_other$bfi_2
bfi_other$bfi_6R <- 6 - bfi_other$bfi_6
bfi_other$bfi_8R <- 6 - bfi_other$bfi_8
bfi_other$bfi_9R <- 6 - bfi_other$bfi_9
bfi_other$bfi_12R <- 6 - bfi_other$bfi_12
bfi_other$bfi_21R <- 6 - bfi_other$bfi_21
bfi_other$bfi_31R <- 6 - bfi_other$bfi_31
bfi_other$bfi_34R <- 6 - bfi_other$bfi_34


bfi_other <- bfi_other %>%
  select(-c(bfi_2, bfi_6, bfi_8, bfi_9, bfi_12, 
            bfi_21, bfi_31, bfi_34))

set.seed(123)
bfi_other_subset1 <- bfi_other %>%
  group_by(TID) %>%
  slice_sample(n = 1) %>%
  ungroup()

set.seed(124)
bfi_other_subset2 <- bfi_other %>%
  group_by(TID) %>%
  slice_sample(n = 1) %>%
  ungroup()

```

**Extraversion - subset 1**
extraversion items: 
bfi_6R + bfi_11 + bfi_16 + bfi_21R + bfi_26 + bfi_31R + bfi_36
```{r}
# Get means and variances
mv <- datasummary(bfi_6R + bfi_11 + bfi_16 + bfi_21R + bfi_26 + bfi_31R + bfi_36 ~ Mean + Var, data = bfi_other_subset1,
                  output = "data.frame")

# Correlation, adding means and variances
datasummary_correlation(bfi_other_subset1[c("bfi_6R", "bfi_11", "bfi_16", "bfi_21R", "bfi_26", "bfi_31R", "bfi_36")],
                        add_columns = mv[-1])

```

```{r}
psych::alpha(bfi_other_subset1[c("bfi_6R", "bfi_11", "bfi_16", "bfi_21R", "bfi_26", "bfi_31R", "bfi_36")])
```

**Agreeableness**
agreeableness items:
bfi_2R + bfi_7 + bfi_12R + bfi_17 
```{r}
# Get means and variances
mv <- datasummary(bfi_2R + bfi_7 + bfi_12R + bfi_17 ~ Mean + Var, data = bfi_other_subset1,
                  output = "data.frame")

# Correlation, adding means and variances
datasummary_correlation(bfi_other_subset1[c("bfi_2R", "bfi_7", "bfi_12R", "bfi_17")],
                        add_columns = mv[-1])

```

```{r}
psych::alpha(bfi_other_subset1[c("bfi_2R", "bfi_7", "bfi_12R", "bfi_17")])
```

**Conscientiousness**
Conscientiousness items: 
bfi_3 + bfi_8R + bfi_13 + bfi_38
```{r}
# Get means and variances
mv <- datasummary(bfi_3 + bfi_8R + bfi_13 + bfi_38 ~ Mean + Var, data = bfi_other_subset1,
                  output = "data.frame")

# Correlation, adding means and variances
datasummary_correlation(bfi_other_subset1[c("bfi_3", "bfi_8R", "bfi_13", "bfi_38")],
                        add_columns = mv[-1])
```

```{r}
psych::alpha(bfi_other_subset1[c("bfi_3", "bfi_8R", "bfi_13", "bfi_38")])
```

**Neuroticism**
Neuroticism items:
bfi_4 + bfi_9R + bfi_14 + bfi_34R
```{r}
# Get means and variances
mv <- datasummary(bfi_4 + bfi_9R + bfi_14 + bfi_34R ~ Mean + Var, data = bfi_other_subset1,
                  output = "data.frame")

# Correlation, adding means and variances
datasummary_correlation(bfi_other_subset1[c("bfi_4", "bfi_9R", "bfi_14", "bfi_34R")],
                        add_columns = mv[-1])
```

```{r}
psych::alpha(bfi_other_subset1[c("bfi_4", "bfi_9R", "bfi_14", "bfi_34R")])
```


**Extraversion - subset 2**
extraversion items: 
bfi_6R + bfi_11 + bfi_16 + bfi_21R + bfi_26 + bfi_31R + bfi_36
```{r}
# Get means and variances
mv <- datasummary(bfi_6R + bfi_11 + bfi_16 + bfi_21R + bfi_26 + bfi_31R + bfi_36 ~ Mean + Var, data = bfi_other_subset2,
                  output = "data.frame")

# Correlation, adding means and variances
datasummary_correlation(bfi_other_subset2[c("bfi_6R", "bfi_11", "bfi_16", "bfi_21R", "bfi_26", "bfi_31R", "bfi_36")],
                        add_columns = mv[-1])

```

```{r}
psych::alpha(bfi_other_subset2[c("bfi_6R", "bfi_11", "bfi_16", "bfi_21R", "bfi_26", "bfi_31R", "bfi_36")])
```

**Agreeableness- subset 2**
agreeableness items:
bfi_2R + bfi_7 + bfi_12R + bfi_17 
```{r}
# Get means and variances
mv <- datasummary(bfi_2R + bfi_7 + bfi_12R + bfi_17 ~ Mean + Var, data = bfi_other_subset2,
                  output = "data.frame")

# Correlation, adding means and variances
datasummary_correlation(bfi_other_subset2[c("bfi_2R", "bfi_7", "bfi_12R", "bfi_17")],
                        add_columns = mv[-1])

```

```{r}
psych::alpha(bfi_other_subset2[c("bfi_2R", "bfi_7", "bfi_12R", "bfi_17")])
```

**Conscientiousness**
Conscientiousness items: 
bfi_3 + bfi_8R + bfi_13 + bfi_38
```{r}
# Get means and variances
mv <- datasummary(bfi_3 + bfi_8R + bfi_13 + bfi_38 ~ Mean + Var, data = bfi_other_subset2,
                  output = "data.frame")

# Correlation, adding means and variances
datasummary_correlation(bfi_other_subset2[c("bfi_3", "bfi_8R", "bfi_13", "bfi_38")],
                        add_columns = mv[-1])
```

```{r}
psych::alpha(bfi_other_subset2[c("bfi_3", "bfi_8R", "bfi_13", "bfi_38")])
```

**Neuroticism**
Neuroticism items:
bfi_4 + bfi_9R + bfi_14 + bfi_34R
```{r}
# Get means and variances
mv <- datasummary(bfi_4 + bfi_9R + bfi_14 + bfi_34R ~ Mean + Var, data = bfi_other_subset2,
                  output = "data.frame")

# Correlation, adding means and variances
datasummary_correlation(bfi_other_subset2[c("bfi_4", "bfi_9R", "bfi_14", "bfi_34R")],
                        add_columns = mv[-1])
```

```{r}
psych::alpha(bfi_other_subset2[c("bfi_4", "bfi_9R", "bfi_14", "bfi_34R")])
```


```{r}
# Replace with your actual alpha values and CIs
alpha_table <- data.frame(
  Trait = c("Extraversion", "Agreeableness", "Conscientiousness", "Neuroticism"),
  
  self_alpha = c(0.857, 0.591, 0.661, 0.708),
  self_ci    = c("[0.82, 0.88]", "[0.52, 0.66]", "[0.59, 0.72]", "[0.65, 0.75]"),
  
  obs1_alpha = c(0.912, 0.720, 0.751, 0.628),
  obs1_ci    = c("[0.89, 0.94]", "[0.67, 0.76]", "[0.71, 0.79]", "[0.57, 0.68]"),
  
  obs2_alpha = c(0.899, 0.722, 0.729, 0.562),
  obs2_ci    = c("[0.87, 0.93]", "[0.68, 0.77]", "[0.69, 0.77]", "[0.48, 0.63]")
)

library(gt)

alpha_table %>%
  gt(rowname_col = "Trait") %>%
  cols_label(
    self_alpha = "Raw α",
    self_ci = "95% CI",
    obs1_alpha = "Raw α",
    obs1_ci = "95% CI",
    obs2_alpha = "Raw α",
    obs2_ci = "95% CI"
  ) %>%
  tab_spanner(label = "Self-Reported", columns = c(self_alpha, self_ci)) %>%
  tab_spanner(label = "Observer-Reported (Subset 1)", columns = c(obs1_alpha, obs1_ci)) %>%
  tab_spanner(label = "Observer-Reported (Subset 2)", columns = c(obs2_alpha, obs2_ci)) %>%
  fmt_number(columns = c(self_alpha, obs1_alpha, obs2_alpha), decimals = 3) %>%
  tab_header(
    title = "Internal Consistency (Cronbach’s α) for Big Five Traits"
  )


```