---
title: "HW6_LuChang"
author: "Chang Lu"
date: "2025-04-29"
output:
  pdf_document:
    latex_engine: xelatex
---
```{r}
library(dplyr)
```


data preparation - self-reported bfi
```{r}
df_self <- read.csv("~/Desktop/conversation/SCFIS-Zoom_Initial_W1_SharedReality 1.csv")

bfi_self <- df_self %>%
  select(I_bfi10_findsfault, I_bfi11_thorough, I_bfi12_depressed, I_bfi13_original, I_bfi21_reserved, 
         I_bfi14_unselfish, I_bfi15_careless, I_bfi16_relaxed, I_bfi1_energy, I_bfi18_quarrels, 
         I_bfi19_reliable, I_bfi20_tense, I_bfi22_deepthinker, I_bfi3_enthusiasm, I_bfi23_forgiving, 
         I_bfi5_quiet, I_bfi7_assertive, I_bfi8_shy, I_bfi4_calm, I_bfi9_outgoing, I_bfi6_makesplans
  ) %>%
  rename(
    bfi_2 = I_bfi10_findsfault,
    bfi_3 = I_bfi11_thorough,
    bfi_4 = I_bfi12_depressed,
    bfi_5 = I_bfi13_original,
    bfi_6 = I_bfi21_reserved,
    bfi_7 = I_bfi14_unselfish,
    bfi_8 = I_bfi15_careless,
    bfi_9 = I_bfi16_relaxed,
    bfi_11 = I_bfi1_energy,
    bfi_12 = I_bfi18_quarrels,
    bfi_13 = I_bfi19_reliable,
    bfi_14 = I_bfi20_tense,
    bfi_15 = I_bfi22_deepthinker,
    bfi_16 = I_bfi3_enthusiasm,
    bfi_17 = I_bfi23_forgiving,
    bfi_21 = I_bfi5_quiet,
    bfi_26 = I_bfi7_assertive,
    bfi_31 = I_bfi8_shy,
    bfi_34 = I_bfi4_calm,
    bfi_36 = I_bfi9_outgoing,
    bfi_38 = I_bfi6_makesplans
  )

#reverse-coded items
bfi_self$bfi_2R <- 6 - bfi_df$bfi_2
bfi_self$bfi_6R <- 6 - bfi_df$bfi_6
bfi_self$bfi_8R <- 6 - bfi_df$bfi_8
bfi_self$bfi_9R <- 6 - bfi_df$bfi_9
bfi_self$bfi_12R <- 6 - bfi_df$bfi_12
bfi_self$bfi_21R <- 6 - bfi_df$bfi_21
bfi_self$bfi_31R <- 6 - bfi_df$bfi_31
bfi_self$bfi_34R <- 6 - bfi_df$bfi_34


bfi_df <- bfi_df %>%
  select(-c(bfi_2, bfi_6, bfi_8, bfi_9, bfi_12, 
            bfi_21, bfi_31, bfi_34))
```


```{r}
df_other <- read.csv("~/Desktop/conversation/SCFIS-Zoom_RR_Final_W1_SharedReality.csv")

bfi_other <- df_other %>%
  select(PID, TID, Order,
         P_bfi10_findsfault, P_bfi11_thorough, P_bfi12_depressed, P_bfi13_original, P_bfi21_reserved, 
         P_bfi14_unselfish, P_bfi15_careless, P_bfi16_relaxed, P_bfi1_energy, P_bfi18_quarrels, 
         P_bfi19_reliable, P_bfi20_tense, P_bfi22_deepthinker, P_bfi3_enthusiasm, P_bfi23_forgiving, 
         P_bfi5_quiet, P_bfi7_assertive, P_bfi8_shy, P_bfi4_calm, P_bfi9_outgoing, P_bfi6_makesplans
  ) %>%
  rename(
    bfi_2 = P_bfi10_findsfault,
    bfi_3 = P_bfi11_thorough,
    bfi_4 = P_bfi12_depressed,
    bfi_5 = P_bfi13_original,
    bfi_6 = P_bfi21_reserved,
    bfi_7 = P_bfi14_unselfish,
    bfi_8 = P_bfi15_careless,
    bfi_9 = P_bfi16_relaxed,
    bfi_11 = P_bfi1_energy,
    bfi_12 = P_bfi18_quarrels,
    bfi_13 = P_bfi19_reliable,
    bfi_14 = P_bfi20_tense,
    bfi_15 = P_bfi22_deepthinker,
    bfi_16 = P_bfi3_enthusiasm,
    bfi_17 = P_bfi23_forgiving,
    bfi_21 = P_bfi5_quiet,
    bfi_26 = P_bfi7_assertive,
    bfi_31 = P_bfi8_shy,
    bfi_34 = P_bfi4_calm,
    bfi_36 = P_bfi9_outgoing,
    bfi_38 = P_bfi6_makesplans
  )

#reverse-coded items
bfi_other$bfi_2R <- 6 - bfi_other$bfi_2
bfi_other$bfi_6R <- 6 - bfi_other$bfi_6
bfi_other$bfi_8R <- 6 - bfi_other$bfi_8
bfi_other$bfi_9R <- 6 - bfi_other$bfi_9
bfi_other$bfi_12R <- 6 - bfi_other$bfi_12
bfi_other$bfi_21R <- 6 - bfi_other$bfi_21
bfi_other$bfi_31R <- 6 - bfi_other$bfi_31
bfi_other$bfi_34R <- 6 - bfi_other$bfi_34


bfi_other <- bfi_other %>%
  select(-c(bfi_2, bfi_6, bfi_8, bfi_9, bfi_12, 
            bfi_21, bfi_31, bfi_34))
```



get covariance matrix
```{r}
cov_matrix <- cov(bfi_df, use = "pairwise.complete.obs")
```

fit the 5 factor model with each item loading on one of the five factors: extraversion, neuroticism, openness, conscientiousness, agreeableness. 
```{r}
library(lavaan)
cfa_mod <- "
    # Loadings
    Extraversion =~ bfi_1 + bfi_6R + bfi_11 + bfi_16 + bfi_21R + bfi_26 + bfi_31R + bfi_36
    Agreeableness =~ bfi_2R + bfi_7 + bfi_12R + bfi_17 + bfi_22 + bfi_27R + bfi_32 + bfi_37R + bfi_42
    Conscientious =~ bfi_3 + bfi_8R + bfi_13 + bfi_18R + bfi_23R + bfi_28 + bfi_33 + bfi_38 + bfi_43R
    Neuroticism =~ bfi_4 + bfi_9R + bfi_14 + bfi_19 + bfi_24R + bfi_29 + bfi_34R + bfi_39
    Openness =~ bfi_5 + bfi_10 + bfi_15 + bfi_20 + bfi_25 + bfi_30 + bfi_35R + bfi_40 + bfi_41R + bfi_44
    # Factor covariances 
    Extraversion ~~ Agreeableness + Conscientious + Neuroticism + Openness
    Agreeableness ~~ Conscientious + Neuroticism + Openness
    Conscientious ~~ Neuroticism + Openness
"

# Default of lavaan::cfa
cfa_fit <- cfa(cfa_mod,
                sample.cov = cov_matrix,
                # number of observations
                sample.nobs = 567,
                # Model identified by standardizing the latent variables
                std.lv = TRUE
)
```

obtain model parameters
```{r}
summary(cfa_fit, fit.measures = TRUE)
```

residuals and modification indices
```{r}
resid(cfa_fit, type = "cor")

modindices(cfa_fit, sort = TRUE, minimum = 10)
```

there are unmodelled correlations between multiple pairs of items, and those items are either quite similar or totally opposite in terms of wording, so I modified my model to account for the unique variances between those pairs
```{r}
cfa_mod_2 <- "
    # Loadings
    Extraversion =~ bfi_1 + bfi_6R + bfi_11 + bfi_16 + bfi_21R + bfi_26 + bfi_31R + bfi_36
    Agreeableness =~ bfi_2R + bfi_7 + bfi_12R + bfi_17 + bfi_22 + bfi_27R + bfi_32 + bfi_37R + bfi_42
    Conscientious =~ bfi_3 + bfi_8R + bfi_13 + bfi_18R + bfi_23R + bfi_28 + bfi_33 + bfi_38 + bfi_43R
    Neuroticism =~ bfi_4 + bfi_9R + bfi_14 + bfi_19 + bfi_24R + bfi_29 + bfi_34R + bfi_39
    Openness =~ bfi_5 + bfi_10 + bfi_15 + bfi_20 + bfi_25 + bfi_30 + bfi_35R + bfi_40 + bfi_41R + bfi_44
    # Unique covariances
    bfi_5 ~~  bfi_25
    bfi_9R ~~ bfi_34R
    bfi_16 ~~ bfi_11
    bfi_30 ~~  bfi_44
    bfi_19 ~~  bfi_39
    bfi_4 ~~ bfi_24R
    bfi_21R ~~ bfi_31R
    bfi_6R ~~ bfi_21R
    bfi_30 ~~ bfi_41R
"

cfa_fit_2 <- cfa(cfa_mod_2,
               sample.cov = cov_matrix,
               # number of observations
               sample.nobs = 567,
               # Model identified by standardizing the latent variables
               std.lv = TRUE
)
```

get model parameters
```{r}
summary(cfa_fit_2, fit.measures = TRUE)
```

Summary:
We fit a 5-factor model with each item loading on one of the five factors: extraversion, openness, conscientiousness, neuroticism, and agreeableness. The item loading specifications are consistent with what's suggested by prior Big Five literature. We used the lavaan package (v0.6.19; Rosseel, 2012) with normal distribution-based maximum likelihood estimation. There were no missing data as all participants responded to all items. We evaluate the model using the global test, as well as goodness-of-fit indices including RMSEA (≤ .05 indicating good fit; Browne & Cudeck, 1993), CFI (≥ .95 indicating good fit; Hu & Bentler, 1999), and SRMR (≤ .08 indicating acceptable fit; Hu & Bentler, 1999). We also consider the correlation residuals and the modification indices.

The test indicated that the hypothesized 5-factor model does not perfectly fit the data, 
(N = 567, df = 892) = 3378, p < .001. The model fit is not ideal either, with RMSEA = .07, 90% CI [.068, .073], CFI = .73, and SRMR = .08. Inspection of the correlation residuals shows relatively large unmodelled correlations between multiple pairs of items, and modification indices similarly suggest adding unique covariance between those pairs of items.

Given that those pairs of items have either similar wordings or totally opposite wordings, we refit the model with unique covariance between them. The model fit improves, (N = 567, df = 883) = 2696, p < .001, RMSEA = .06, 90% CI [.058, .063], CFI = .81, and SRMR = .08. Further inspection of correlation residuals and modification indices does not suggest modifications to the model that are theoretically justified.
